\textit{Supplementary materials for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2021-08-02 paper/main.tex
PR updates

  \paragraph*{Ramping.}  We generated a third set of 100 synthetic
  datasets whose underlying correlations changed gradually over time.
  For each dataset, we constructed two anchor covariance
  matrices using Equation~\ref{eqn:randcorr},
  $\mathbf{\Sigma}_{\mathrm{start}}$ and
  $\mathbf{\Sigma}_{\mathrm{end}}$.  For each of the 300 timepoints in
  each dataset, we drew the observations from a multivariate Gaussian
  distribution whose covariance matrix at each timepoint $t \in
  \left[0, ..., 299\right]$ was given by
  \begin{align}
    \mathbf{\Sigma}_t = \left( 1 - \frac{t}{299} \right)
    \mathbf{\Sigma}_{\mathrm{start}} + \frac{t}{299}\mathbf{\Sigma}_{\mathrm{end}}.
  \end{align}
The gradually changing correlations underlying these datasets allow us
to evaluate the recovery of dynamic correlations when each timepoint's
correlation matrix is unique (as in the random datasets), but where
the correlation dynamics are structured and exhibit first-order
autocorrelations (as in the constant datasets).

@@

Given a timeseries of $n$\textsuperscript{th}-order correlations, we
then need to work ``backwards'' in order to generate the order-zero
timeseries.  If the $n$\textsuperscript{th}-order correlation matrix
at a given timepoint is $m_n$, then we can generate an order $n-1$
correlation matrix (for $n > 1$) by taking a draw from
$\mathcal{N}\left(0, m_n\right)$ and reshaping the resulting vector to
have square dimensions.  Intuitively, the re-shaped matrix will look
like a noisy version of the template matrix, $m_{n-1}$.  (When
$n = 1$, no re-shaping is needed; the resulting $K$-dimensional vector
may be used as the observation at the given timepoint.)  After
independently drawing each timepoint's order $n-1$ correlation matrix
from that timepoint's order $n$ correlation matrix, this process can
be applied repeatedly until $n = 0$.  This results in a
$K$-dimensional timeseries of $T$ observations containing the
specified high-order correlations at orders 1 through $n$.  Following
our approach to generating synthetic data exhibiting known first-order
correlations, we constructed a total of 400 additional multivariate
timeseries, collectively reflecting a total of 4 qualitatively
different patterns of dynamic correlations (i.e., 100 datasets
reflecting each type of dynamic pattern: constant, random, ramping,
and event).  Each timeseries comprised 10 features (dimensions)
that varied over 300 timepoints for first-order correlations, and
therefore 100 second-order features.

\subsubsection*{Functional neuroimaging data collected during story
  listening}
We examined an fMRI dataset collected by \cite{SimoEtal16} that the
authors have made publicly available at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.  The dataset
comprises neuroimaging data collected as participants listened
to an audio recording of a story (intact condition; 36 participants),
listened to temporally scrambled recordings of the same story (17
participants in the paragraph-scrambled condition listened to the
paragraphs in a randomized order and 36 in the word-scrambled
condition listened to the words in a randomized order), or lay resting
with their eyes open in the scanner (rest condition; 36
participants).  Full neuroimaging details may be found in the original
paper for which the data were collected~\citep{SimoEtal16}. Procedures were approved by the Princeton University Committee on Activities Involving Human Subjects, and by Western Institutional Review Board (Puyallup, WA). All subjects were native English speakers with normal hearing and provided written informed consent.

@@

All of our analysis code may be downloaded from\href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.

>>>>

  \paragraph*{Ramping.}  We generated a third set of 100 synthetic
  datasets whose underlying correlations changed gradually over time.
  For each dataset, we constructed two``anchor'' covariance
  matrices using Equation~\ref{eqn:randcorr},
  $\mathbf{\Sigma}_{\mathrm{start}}$ and
  $\mathbf{\Sigma}_{\mathrm{end}}$.  For each of the 300 timepoints in
  each dataset, we drew the observations from a multivariate Gaussian
  distribution whose covariance matrix at each timepoint $t \in
  \left[0, ..., 299\right]$ was given by
  \begin{align}
    \mathbf{\Sigma}_t = \left( 1 - \frac{t}{299} \right)
    \mathbf{\Sigma}_{\mathrm{start}} + \frac{t}{299}\mathbf{\Sigma}_{\mathrm{end}}.
  \end{align}
The gradually changing correlations underlying these datasets allow us
to evaluate the recovery of dynamic correlations when each timepoint's
correlation matrix is unique (as in the random datasets), but where
the correlation dynamics are structured and exhibit first-order
autocorrelations (as in the constant datasets).

@@

Given a timeseries of $n$\textsuperscript{th}-order correlations, we
then need to work ``backwards'' in order to generate the order-zero
timeseries.  If the $n$\textsuperscript{th}-order correlation matrix
at a given timepoint is $m_n$, then we can generate an order $n-1$
correlation matrix (for $n > 1$) by taking a draw from
$\mathcal{N}\left(0, m_n\right)$ and reshaping the resulting vector to
have square dimensions.  To force the resulting matrix to be
symmetric, we remove its lower triangle, and replace the lower
triangle with (a reflected version
of) its upper triangle. Intuitively, the re-shaped matrix will look
like a noisy (but symmetric) version of the template matrix, $m_{n-1}$.  (When
$n = 1$, no re-shaping is needed; the resulting $K$-dimensional vector
may be used as the observation at the given timepoint.)  After
independently drawing each timepoint's order $n-1$ correlation matrix
from that timepoint's order $n$ correlation matrix, this process can
be applied repeatedly until $n = 0$.  This results in a
$K$-dimensional timeseries of $T$ observations containing the
specified high-order correlations at orders 1 through $n$.  Following
our approach to generating synthetic data exhibiting known first-order
correlations, we constructed a total of 400 additional multivariate
timeseries, collectively reflecting a total of 4 qualitatively
different patterns of dynamic correlations (i.e., 100 datasets
reflecting each type of dynamic pattern: constant, random, ramping,
and event).   Each timeseries comprised 10 zero-order features (dimensions)
that varied over 300 timepoints.  After applying our dynamic
correlation estimation procedure, this yielded a 100-dimensional
timeseries of first-order
features that could then be used to estimate dynamic second-order
correlations.  (We chose to use $K=10$ zero-order features for our
higher order simulations in order to put the accuracy computations
displayed in Figs.~\ref{fig:synthetic} and~\ref{fig:higher_order_sims}
on a roughly even footing.)

\subsubsection*{Functional neuroimaging data collected during story
  listening}
We examined an fMRI dataset collected by \cite{SimoEtal16} that the
authors have made publicly available at
\href{http://arks.princeton.edu/ark:/88435/dsp015d86p269k}{arks.princeton.edu/ark:/88435/dsp015d86p269k}.  The dataset
comprises neuroimaging data collected as participants listened
to an audio recording of a story (intact condition; 36 participants),
listened to temporally scrambled recordings of the same story (17
participants in the paragraph-scrambled condition listened to the
paragraphs in a randomized order and 36 in the word-scrambled
condition listened to the words in a randomized order), or lay resting
with their eyes open in the scanner (rest condition; 36
participants).  Full neuroimaging details may be found in the original
paper for which the data were collected~\citep{SimoEtal16}. Procedures
were approved by the Princeton University Committee on Activities
Involving Human Subjects, and by the Western Institutional Review Board (Puyallup, WA). All subjects were native English speakers with normal hearing and provided written informed consent.

@@

All of our analysis code may be downloaded from \href{https://github.com/ContextLab/timecorr-paper/releases/tag/v0.3}{github.com/ContextLab/timecorr-paper/releases/tag/v0.3}.

### 2021-08-02 paper/supplementary_materials.tex
PR updates

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/decode_levels_kernels}
\caption{\textbf{Across-participant timepoint decoding accuracy varies with
      correlation order and cognitive engagement across kernels.}
    \textbf{a.-c.~Timepoint decoding accuracy as a function of order: PCA.} Order ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    Feature weighting and testing).  The reported
    across-participant decoding accuracies for \textbf{a. Gaussian},
    \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernel shapes are averaged over all
   widths (see Identifying robust decoding
      results).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
    denote 95\% confidence intervals of the mean across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upward
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed $t$-test, thresholded at
    $p < 0.05$, exact values are reported in the Source Data file).  The circled values represent
    the maximum decoding accuracy within each experimental
    condition. Panels a.-c. used PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space. \textbf{d.-f.~Timepoint decoding accuracy as a
      function of order: eigenvector centrality.} These panels are in the
    same format as Panel a.-c., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations into lower-dimensional spaces. Source data are provided as a Source Data file.}
\label{fig:supp_kernels}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/decode_levels_widths}
\caption{\textbf{Across-participant timepoint decoding accuracy varies with
      correlation order and cognitive engagement across widths.}
    \textbf{a.-d.~Timepoint decoding accuracy as a function of order: PCA.} Order ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    Feature weighting and testing).  The reported
    across-participant decoding accuracies for kernel widths of \textbf{a. 5},
    \textbf{b. 10}, \textbf{c. 20}, and \textbf{d. 50} are averaged over all
    kernel shapes (see Identifying robust decoding
      results).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
    denote 95\% confidence intervals of the mean across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upward
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed $t$-test, thresholded at
    $p < 0.05$, exact values are reported in the Source Data file).  The circled values represent
    the maximum decoding accuracy within each experimental condition.  Panels a.-d. used PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.\textbf{e.-h.~Timepoint decoding accuracy as a
      function of order: eigenvector centrality.} These panels are in the
    same format as Panel a.-d., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations into lower-dimensional spaces.  Source data are provided as a Source Data file.}
\label{fig:supp_widths}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_time}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across time and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices.
    The averages are taken across several randomly generated
    synthetic datasets for each timeseries pattern (constant, random,
    ramping, and data; see Synthetic data: simulating dynamic higher-order
      correlations).  The $x$-axes of each heatmap denote varying
    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
    denote varying durations (in samples) of the synthetic datasets.
    A total of 10 synthetic datasets were generated for each duration
    (row) and timeseries pattern (panel).  Source data are provided as a Source Data file.}
\label{fig:time}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across features and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices.
    The averages are taken across several randomly generated
    synthetic datasets for each timeseries pattern (constant, random,
    ramping, and data; see Synthetic data: simulating dynamic higher-order
      correlations).  The $x$-axes of each heatmap denote varying
    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
    denote varying numbers of features ($K$) used in each of the synthetic datasets.
    A total of 10 synthetic datasets were generated for each number of features
    (row) and timeseries pattern (panel). Source data are provided as a Source Data file.}
\label{fig:features}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the intact experimental
    condition.}  Each color corresponds to one order of inter-subject
functional correlations. The inflated brain plots display the
locations of the endpoints of the 10 strongest (absolute value)
correlations at each order, projected onto the cortical
surface~\citep{CombEtal19}.  The lists of terms display
the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
top row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the paragraph experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
second row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the word experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
third row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the rest experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  resting state condition.  (Also see Fig.~\neurosynth,
bottom row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:rest}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/pca}
\caption{\textbf{Cumulative percent variance explained as a function
    of the number of principle components.}  Order refers to the order of the dynamic
    correlations calculated. Principle components analysis was
    performed, and reduced independently for each subject.  Maximum number of components varies with
    the total time for each condition (intact: 300; paragraph: 272;
    word: 300; rest: 400). \textbf{a.~Cumulative percent
    variance as a function of number of components for Order 0.} PCA
  was performed on the raw activity patterns (Order 0). \textbf{b.-e.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.:
    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels are in the
    same format as Panel b.-e., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space. Source data are provided as a Source Data file.}
\label{fig:pca}
\end{figure}

>>>>

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/decode_levels_kernels}
\caption{\textbf{Across-participant timepoint decoding accuracy varies with
      correlation order and cognitive engagement across kernels.}
    \textbf{a.-c.~Timepoint decoding accuracy as a function of order:
      PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    \textit{Feature weighting and testing}).  The reported
    across-participant decoding accuracies for \textbf{a. Gaussian},
    \textbf{b. Laplace}, and \textbf{c. Mexican hat} kernel shapes are averaged over all
   widths (see \textit{Identifying robust decoding
      results}).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
    denote 95\% confidence intervals of the mean across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upward
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed $t$-test, thresholded at
    $p < 0.05$; exact values are reported in the Source Data file).  The circled values represent
    the maximum decoding accuracy within each experimental
    condition. Panels a.-c. used PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space. \textbf{d.-f.~Timepoint decoding accuracy as a
      function of order: eigenvector centrality.} These panels are in the
    same format as Panel a.-c., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations into lower-dimensional spaces. Source data are provided as a Source Data file.}
\label{fig:supp_kernels}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/decode_levels_widths}
\caption{\textbf{Across-participant timepoint decoding accuracy varies with
      correlation order and cognitive engagement across widths.}
    \textbf{a.-d.~Timepoint decoding accuracy as a function of order:
      PCA.} \textit{Order} ($x$-axis) refers to the maximum order of dynamic
    correlations that were available to the classifiers (see
    Feature weighting and testing).  The reported
    across-participant decoding accuracies for kernel widths of \textbf{a. 5},
    \textbf{b. 10}, \textbf{c. 20}, and \textbf{d. 50} are averaged over all
    kernel shapes (see Identifying robust decoding
      results).  The $y$-values are displayed relative to chance
    accuracy (intact: $\frac{1}{300}$; paragraph: $\frac{1}{272}$;
    word: $\frac{1}{300}$; rest: $\frac{1}{400}$).  The error ribbons
    denote 95\% confidence intervals of the mean across cross-validation folds
    (i.e., random assignments of participants to the training and test
    sets).  The colors denote the experimental condition.  Arrows
    denote sets of features that yielded reliably higher (upward
    facing) or lower (downward facing) decoding accuracy than the mean
    of all other features (via a two-tailed $t$-test, thresholded at
    $p < 0.05$; exact values are reported in the Source Data file).  The circled values represent
    the maximum decoding accuracy within each experimental condition.  Panels a.-d. used PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.\textbf{e.-h.~Timepoint decoding accuracy as a
      function of order: eigenvector centrality.} These panels are in the
    same format as Panel a.-d., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations into lower-dimensional spaces.  Source data are provided as a Source Data file.}
\label{fig:supp_widths}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_time}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across time and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices.
    The averages are taken across several randomly generated
    synthetic datasets for each timeseries pattern (constant, random,
    ramping, and data; see \textit{Synthetic data: simulating dynamic higher-order
      correlations}).  The $x$-axes of each heatmap denote varying
    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
    denote varying durations (in samples) of the synthetic datasets.
    A total of 10 synthetic datasets were generated for each duration
    (row) and timeseries pattern (panel).  Source data are provided as a Source Data file.}
\label{fig:time}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.95\textwidth]{figs/sim_heatmaps_features}
  \caption{\textbf{Recovery heatmap of simulated first-order and
      second-order dynamic correlations across features and widths.}  Each panel displays a
    heatmap of the average correlations
    between the vectorized upper triangles of the recovered
    first-order and second-order correlation matrices and the true
    (simulated) first-order and second order correlation matrices.
    The averages are taken across several randomly generated
    synthetic datasets for each timeseries pattern (constant, random,
    ramping, and data; see \textit{Synthetic data: simulating dynamic higher-order
      correlations}).  The $x$-axes of each heatmap denote varying
    Laplace-shaped kernel widths (see Figs.~\ref{fig:supp_kernels}
    and~\ref{fig:supp_widths}), and the $y$-axes of each heatmap
    denote varying numbers of features ($K$) used in each of the synthetic datasets.
    A total of 10 synthetic datasets were generated for each number of features
    (row) and timeseries pattern (panel). Source data are provided as a Source Data file.}
\label{fig:features}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the \textit{intact} experimental
    condition.}  Each color corresponds to one order of inter-subject
functional correlations. The inflated brain plots display the
locations of the endpoints of the 10 strongest (absolute value)
correlations at each order, projected onto the cortical
surface~\citep{CombEtal19}.  The lists of terms display
the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
top row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the \textit{paragraph} experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
second row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the \textit{word} experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
third row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
\caption{\textbf{Top terms associated with the most strongly
      correlated nodes at each order, for the \textit{rest} experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  resting state condition.  (Also see Fig.~\neurosynth,
bottom row, in the main text.) Source data are provided as a Source Data file.}
\label{fig:rest}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/pca}
\caption{\textbf{Cumulative percent variance explained as a function
    of the number of principle components.}  \textit{Order} refers to the order of the dynamic
    correlations calculated. Principle components analysis was
    performed, and reduced independently for each subject.  Maximum number of components varies with
    the total time for each condition (intact: 300; paragraph: 272;
    word: 300; rest: 400). \textbf{a.~Cumulative percent
    variance as a function of number of components for Order 0.} PCA
  was performed on the raw activity patterns (Order 0). \textbf{b.-e.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.:
    PCA} Dynamic correlation were calculated for orders 1-4 using PCA to
    project each high-dimensional pattern of dynamic correlations onto
    a lower-dimensional space.   \textbf{f.-i.~Cumlative percent
    variance as a function of number of components for Orders 1.-4.: eigenvector centrality.} These panels are in the
    same format as Panel b.-e., but here eigenvector centrality has been
    used to project the high-dimensional patterns of dynamic
    correlations onto a lower-dimensional space. Source data are provided as a Source Data file.}
\label{fig:pca}
\end{figure}
